Uncertain Effects of DFT Functionals on Charge Dynamic of Organic Semiconductor

### 2024-10-16 paper.tex
update

\begin{document}
\linenumbers
\title{Uncertain Effects of DFT Functionals on Charge Dynamic of Organic Semiconductor }
\author{authors}
\date{\today}
\maketitle
\begin{abstract}
In this paper, the time-of-flight (ToF) is used to quantify the charge mobility in OSC. 
Using ToF as the quantity of interest, the uncertainty effect of the DFT functionals on the ToF in a BCP device is studied. 
Using a total of 10 different DFT functionals, we find that the electronic structure properties have similar distributions as indicated by Wasserstein distance, while the ToF can have a relatively large deviation.
Further investigation reveals that ToF can be sensitive to the energy of a single molecule, leading to the ToF being sensitive to DFT functionals.

Further investigation reveals that the BHANDHLYP functional leads to a trap site, and the charge mobility is very sensitive to the trap sites' energy, so a small change in the site's energy results in a large deviation of ToF.  
We further estimate the charge mobility distribution due to the uncertainty in electronic structure properties, and those properties' uncertainty is obtained from the maximum likelihood estimation of the 10 data points calculated using the 10 DFT functionals.
Ultimately, a confidence level of charge mobility is obtained, and it is found that the uncertainty in site energy has the most significant effect on the ToF. 
\end{abstract}

@@

The charge dynamics is determined by CTRW transition rates, which depend on the electronic structures.
Since DFT is used to calculate the molecular electronic structures, the unknown exchange-correlation functional in DFT will bring uncertainties to the multiscale model. 
In particular, different DFT functionals contain varying levels of Hartree Fock (HF) to represent the exchange-correlation potential. 
The effect of the uncertainty from the DFT exchange-correlation functional on the multiscale model is not yet explored in literatures. 
The goal of this work is to quantify the uncertainty effect of the DFT exchange-correlation functional on the charge dynamics in OSCs and to study the robustness of the multiscale model.

@@

Specifically, the focus will be placed on following questions: 
\begin{enumerate}
    \item How do DFT functionals change the electronic structures: reorganization energy, distribution of molecule energies and coupling elements? 
    \item How do DFT functionals change the charge mobility?
    \item Which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the charge mobility distribution?
    \item Can we estimate the range of the quantity of interest, given a confidence level?
\end{enumerate}

@@

To calculate $v_\text{SS}$ the steady state distribution $\pi_i$ is required. In continuous time Markov chain, the steady state distribution vector $\vec{\pi}: \pi_i$ is the null-space of $\mathbf{W}-\mathbf{D}$:
\begin{equation}
    (\mathbf{W}-\mathbf{D} )\vec{\pi} = \mathbf{0}
\end{equation}
where $\mathbf{D} = \text{diag}(D_i)$ is the out-degree matrix of $\mathbf{W}$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results on BCP}
\label{sec:result}

A OSC device consisting of 1000 BCP molecules arranged in $8 \times 8 \times 8$ cubic box is simulated using MD, as shown in Fig. \ref{fig:MSM}(a).
The \textit{Source} contains molecules whose COM have X-coordinates $0 < r^x_i < 0.5$ nm, and \textit{Sink} molecules $7.5 < r^x_i < 8$. 
This section presents the molecule energy distribution, coupling element distribution, reorganization energies and ToFs calculated using the 10 DFT functionals. 
Using the PBE0 functional as a reference, the difference in electronic structure distributions due to DFT functionals is measured by the Wasserstein distance. In contrast to the small Wasserstein distance between the electronic structure distributions, the difference in ToF $\Delta \tau$ is relatively large. 
Next, the change of the graph connectivity due to different DFT functionals is used to explain the $\Delta \tau$.
Following this, a normal distribution estimated from maximum likelihood is used to represent the uncertainty in each electronic structure parameters. Then distributions of ToF are obtained using the electronic structure parameters generated by Monte Carlo sampling from the estimated distributions. Finally, the sensitivities of $E_i,J_{ij},\lambda_{ij}$ to ToF are compared, confidence level of ToFs are estimated.

\subsection{Electronic Structure Parameters and ToFs}
Using ten different functionals, the molecule energies, coupling elements and reorganization energies are calculated from the multiscale model with ten different DFT functional.

Table \ref{tab:para} summarizes the names of the DFT functionals, the amount of Hartree-Fock exchange (HFX), the reorganization energies, ToFs, the standard deviation of the molecule energy distributions, the drift ToFs under an electric field $6 \times 10^7$ V/m and mobility.
The table indicates that while the energy standard deviations $\sigma(E)$ are similar across different functionals, the ToF vary significantly, notably for functionals like BHANDHLYP, M06L, and BHLYP.

\begin{table}[H]
    \centering
    \begin{tabular}{c c c c c c c}
    \hline
        Functional & HFX & $\lambda_{ij}$ [eV] & ToF [s] & $\sigma(E)$ & drift ToF [s] & $\mu$ [m/s] \\ 
        \hline
        PBE0 & 0.25 & 0.388 & $1.23\times 10^{-3}$ & 0.175 & $1.44 \times 10^{-6}$ & $9.40\times 10^{-7}$ \\
        PBE & 0 & 0.303 & $1.04\times 10^{-3}$ & 0.172 & $2.27 \times 10^{-7}$ & $5.95 \times 10^{-6}$ \\ 
        B3LYP & 0.20 & 0.375 & $4.28\times 10^{-3}$ & 0.175  & $3.22\times 10^{-7}$ & $4.08 \times 10^{-6}$ \\
        BHANDHLYP & 0.5 & 0.494 & \textbf{737.94} & 0.192  & $4.75\times 10^{-2}$ & $2.86\times 10^{-11}$ \\
        TPSS & 0 & 0.310 & $1.37\times 10^{-2}$ & 0.168  & $1.03 \times 10^{-6}$ & $1.30\times 10^{-7}$ \\
        BP86 & 0 & 0.304 & $7.46\times 10^{-3}$ & 0.175  & $5.81 \times 10^{-7}$ & $2.33\times 10^{-6}$ \\
        wB97X & 0.157 & 0.505 & $2.92\times 10^{-2}$ & 0.191  & $2.01\times 10^{-6}$  & $6.74\times 10^{-7}$ \\
        wB97X-D3 & 0.195 & 0.496 & $4.89\times 10^{-2}$ & 0.180  & $2.50 \times 10^{-6}$ & $5.42 \times 10^{-7}$ \\
        M06L & 0 & 0.312 & 0.319 & 0.165 & $2.11 \times 10^{-5}$ & $6.42 \times 10^{-8}$ \\
        BHLYP & 0.5 & 0.493 & 2.47 & 0.192  & $5.96 \times 10^{-5}$ & $ 2.28\times 10^{-8}$  \\
    \hline
    \end{tabular}
    \caption{DFT functional HF exchange scaling (HFX), calculated values of reorganization energy ($\lambda_{ij}$), diffusive ToF, energy disorder ($\sigma(E)$), drift ToF, and mobility ($\mu$) for BCP molecules for different DFT functionals.}
    \label{tab:para}
\end{table}

The functional BHANDHLYP gives a ToF much larger than the rest of the 9 functionals. 
The reason for this large ToF in BHANDHLYP is that one molecule has relatively low energy, and the out-going rate for this molecule is very small, eventually leading to large ToF. 
However, such large difference in a material system is non-physical, and studying the uncertain quantification based on those ToF data can not indicate anything on the robustness of the multiscale model.

A noticeable difference in all the different functional is the amount of HF for approximating the exchange-correlations. 
The large HFX cases (BHANDHLYP and BHLYP) have large ToF, while other functionals have smaller HFX. In commonly practices, most functionals use small HFX.

In our next step, the functional is fixed to be the commonly used PBE0 functional, the HFX is varied to investigate the effect of HFX on the molecular properties and ToF.

\subsection{BCP molecule with different HFX}
Our first investigation use the range of HFX=$0.05,0.15,0.23,0.24,0.25,0.26,0.27,0.35,0.45,0.55$. The values of HFX=$0.23,0.24,0.26,0.27$ are used because we want to see if a small perturbation in HFX would affect ToF significantly.

Since ToF is sensitively affected by site energy, which is affected by the isotropic polarizability $P_\text{iso}$ and dipole moment $\mu$ of the molecules, we plot the those molecular properties as a function of HFX. 
\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\textwidth]{figs/BCP_HFX/fig_autogen_BCP.pdf}
    \caption{(a) The neutral state BCP molecule dipole moment $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters. }
    \label{fig:autogen}
\end{figure}
The Fig.\ref{fig:autogen}(a) shows that as HFX increase, the dipole moment increases first linear in the range of HFX=0.05 to 0.35, then a relatively large increase at HFX=0.35 to 0.55.

Figure \ref{fig:autogen}(b) shows that as HFX increase, the n state and h state BCP molecule has decreasing isotropic polarizability, showing that the molecule is getting more difficult to be polarized. 
However, the change of $P_\text{iso}$ is more dramatic in the h state molecules. 
Since the difference between the n state $P_\text{iso}$ and h state $P_\text{iso}$ is getting smaller, the contribution of polarizability effect on the energy disorder is weaker. This results in a large energy disorder as HFX increase.

Fig.\ref{fig:autogen}(c) shows that as HFX increase, reorganization energies are higher. Since the molecule requires more energy to reorient itself during the charge transfer process, the higher reorganization energy can potentially slow down charge transport when there is no energy disorder present.

Fig.\ref{fig:autogen}(d) shows that when HFX=0.05-0.3 the energy disorder is relatively small (less than 0.2 eV). When HFX=0.35-0.55, the energy disorder $\sigma(E)>0.22$. This pattern is consistent with the change of $P_\text{iso}$ as shown in Fig. \ref{fig:autogen}(b)

The ToF of the BCP molecular system calculated using different HFX is shown in table \ref{tab:ToF_BCP_HFX}. This table shows that for HFX=0.35,0.45,0.55, the ToFs are extremely large compared to the ToFs for HFX<0.3. 
In contrast to the almost linear HFX-$\lambda$ relationship, those large ToFs are not physical.

\begin{table}[H]
    \centering
    \begin{tabular}{c c c c c}
    \hline
        HFX & ToF [s] & $v_\text{ToF}$ [m/s] & ToF(no $E$) [s] & $v_\text{ToF}$(no $E$) [m/s] \\
    \hline
        0.05 & 0.32 & $2.2 \times 10^{-8}$ & $3.0 \times 10^{-10}$ & 24 \\
        0.15 & 0.39 & $1.8 \times 10^{-8}$ & $4.7 \times 10^{-10}$ & 15 \\
        0.23 & 0.020 & $3.6 \times 10^{-7}$ & $6.8 \times 10^{-10} $ & 10 \\
        0.24 & 0.030 & $2.4 \times 10^{-7}$ & $7.0 \times 10^{-10} $ & 10 \\
        0.25 & 0.026 & $2.7 \times 10^{-7}$ & $7.6 \times 10^{-10}$ & 9.4 \\
        0.26 & 3.2 & $4.5 \times 10^{-9}$ & $7.8 \times 10^{-10}$ & 22 \\
        0.27 & 0.036 & $2.0 \times 10^{-7}$ & $9.2 \times 10^{-10}$ & 7.8 \\
        0.35 & $1.7 \times 10^7 $ & $4.1 \times 10^{-16}$ & $1.0 \times 10^{-9}$ & 7.1 \\
        0.45 & $1.8 \times 10^4$ & $3.6 \times 10^{-12}$ & $1.3 \times 10^{-9}$ & 5.4\\
        0.55 & $1.2 \times 10^9 $ & $5.7 \times 10^{-18}$ & $1.9 \times 10^{-9} $ & 3.8 \\
    \hline
    \end{tabular}
    \caption{The ToF and diffusive velocity calculated by ToF along a distance $L_x = 7.1$ [nm] with and without energy disorder of the BCP system as a function of the HFX. }
    \label{tab:ToF_BCP_HFX}
\end{table}

The reason for this non-physical ToF is that some molecules have extremely small calculated energies.

BCP contains two N atoms which are very difficult to be polarized, resulting the BCP molecule energy and the Thole model being very sensitive to the atomic charges and polarizability.

Furthermore, each molecule in the BCP system has its own topology with different atomic charges and polarizability compared to the optimized BCP structure.  
Those factors result in the fact that when the atomic charges or polarizability exceeds a certain range, the energy calculation will be very non-physical.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\textwidth]{figs/BCP_HFX/scatterE_qmmm.pdf}
    \caption{Scatter plot of BCP site energy calculated from different HFX, compared to the site energy calculated from HFX=0.25 (The PBE0 functional). The brighter color near the diagonal lines indicates denser population of the molecules.  The top and right histogram show the energy distributions.}
    \label{fig:E_qmmm_BCP}
\end{figure}

Figure \ref{fig:E_qmmm_BCP} shows that the molecule energy calculated by the PBE0 functional has a range of -0.3 to -1.7 eV. When $ 0.05 \leq HFX \leq 0.27 $, the molecule energies also have a range of -0.3 to -1.7 eV.

For HFX=0.35,0.45, there are molecules energies close to -2.0 eV, and for HFX=0.55, there is one molecule energy being relatively far from the diagonal line. 
Those mentioned low molecules results in the large energy disorder $\sigma(E)$ as shown in table \ref{tab:para}. 
and they are very different from other energies obtained by $ 0.05 \leq \text{HFX} \leq 0.27 $.

Molecule energy are determined by the atomic charges and polarizability. Those physical properties as shown in Fig.\ref{fig:autogen} follow is linearly dependent on HFX. Since molecular energy for individual molecule are similar as shown by the scatter points cluster around the diagonal line, the deviated molecule energy for HFX=0.35,0.45,0.55 are non-physical. 
When those low energies molecules are filled by charge carriers, the ToF has a huge change and become close to the ToF obtained by $0.05 \leq \text{HFX} \leq 0.27$.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\textwidth]{figs/BCP_HFX/scatterEstat_qmmm.pdf}
    \caption{Scatter plot of BCP electrostatic energy calculated from different HFX, compared to the electrostatic energy calculated from HFX=0.25 (The PBE0 functional). The brighter color near the diagonal lines indicates denser population of the molecules.  The top and right histogram show the energy distributions.}
    \label{fig:Estat_qmmm_BCP}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\textwidth]{figs/BCP_HFX/scatterEdip_qmmm.pdf}
    \caption{Scatter plot of BCP polarization energy calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional). The brighter color near the diagonal lines indicates denser population of the molecules.  The top and right histogram show the energy distributions.}
    \label{fig:Edip_qmmm_BCP}
\end{figure}

The molecule energy has the contribution from the electrostatic effect and polarization effect due to the dipole moment of the molecules. To further understand how the HFX affect molecule energy, the comparison scatter plots of electrostatic energy and polarization energy are shown in Fig.\ref{fig:Estat_qmmm_BCP} and Fig.\ref{fig:Edip_qmmm_BCP}.

Figure \ref{fig:Estat_qmmm_BCP} shows that for all HFX parameters, the electrostatic energy has a range of 0.2 to -1.3 eV. Different $0.05 \leq \text{HFX} \leq 0.55$ values produce relatively close electrostatic energy compared to that of HFX=0.25. 
The large HFX$>0.27$ does not cause deviated electrostatic energy.

Figure \ref{fig:Edip_qmmm_BCP} shows that polarization energy has a range of -0.3 to -1.0 eV. When $0.05 \leq \text{HFX} \leq 0.27$, the polarization energies are very close and the scatter points are cluster along the diagonal line. 
In contrast to the electrostatic energy, Fig.\ref{fig:Edip_qmmm_BCP} shows that for HFX=0.35,0.45,0.55, there are molecules that have small polarization energy, contributing to the small site energies, and the extremely large ToF.

Those small polarization energies and site energies are not physical, because 
when HFX is varied, the change of the polarizability and reorganization energy are almost linear.
In contrast, there is huge jumps in those site energies due to the huge jumps in the polarization energy.

In conclustion, the HFX affects the molecular polarizability, which affects the polarization energies and eventually leads to non-physical molecule energy. 
And large range of HFX leads to non-physical results. 
In the next section, we will use the range with small HFX values for the investigation of a less disorder molecular system, MADN.

\section{Results on MADN}
MADN (2-Methyl-9,10-di(naphth-2-yl)anthracene) is another type of OSC. MADN has more efficient hole transport compared to BCP. 
\begin{table}[H]
    \centering
    \begin{tabular}{c c c c c}
    \hline
        HFX & ToF [s] & $v_\text{ToF}$ [m/s] & ToF(no $E$) [s] & $v_\text{ToF}$ (no $E$) [m/s] \\
    \hline
        0.00 &  $6.4 \times 10^{-9}$ & 1.2 & $1.9 \times 10^{-10}$ & 42 \\
        0.05 & $ 7.9 \times 10^{-9}$ & 1.0 & $4.1 \times 10^{-10}$ & 20 \\
        0.10 & $ 1.6 \times 10^{-8}$ & 0.51 & $4.0 \times 10^{-10} $ & 20 \\
        0.15 & $ 3.0 \times 10^{-8}$ & 0.31 & $4.0 \times 10^{-10} $ & 25 \\
        0.20 & $ 2.1 \times 10^{-8}$ & 0.39 & $4.5 \times 10^{-10}$ & 18 \\
        0.25 & $ 9.5 \times 10^{-8}$ & 0.083 & $7.2 \times 10^{-10}$ & 11 \\
    \hline
    \end{tabular}
    \caption{The ToF and diffusive velocity calculated by ToF along a distance $L_x = 8$ [nm] with and without energy disorder of the MADN system as a function of the HFX. }
    \label{tab:ToF_MADN_HFX}
\end{table}
Table \ref{tab:ToF_MADN_HFX} shows the ToF and $v_\text{ToF}$ obtained with and without energy disorder. 
Compared to the mobility of BCP, MADN has significantly larger $v_\text{ToF}$. When the molecule energy are not considered, $v_\text{ToF}$ of MADN is close to that of BCP. 
So the better hole mobility, that is the larger $v_\text{ToF}$ in MADN compared to BCP is accredited to the energy disorder. 
As HFX increase from 0 to 0.25, the ToF with and without energy disorder increase eventually by a factor of around 10.

Figure \ref{fig:autogen_MADN} shows the dipole moment $\mu$, isotropic polarizability $P_\text{iso}$,  reorganization energies $\lambda$ and energy disorder $\sigma(E)$ as a function of the HFX parameters.
%
\begin{figure}[H]
    \centering
    \includegraphics[width=0.80\textwidth]{figs/MADN_HFX/fig_autogen.pdf}
    \caption{(a) The dipole moment of neutral state MAND molecule $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters.}
    \label{fig:autogen_MADN}
\end{figure}
%

Fig.\ref{fig:autogen_MADN}(a) shows that the dipole moment decreases as HFX increase. At HFX=0.25, there is a relatively sharp decrease. This HFX effect on dipole moment is opposite to that of the BCP molecule, which has the dipole moment increases as the HFX increases.

Fig.\ref{fig:autogen_MADN}(b) shows that the isotropic polarizability for n and h state MADN molecule decrease linearly as HFX increase from 0 to 0.25. 
So the molecules are getting more difficult to be polarized. 
Accordingly, the reorganization energy also increases as HFX increases as shown by Fig.\ref{fig:autogen_MADN}(c). This increase is nonlinear compared to the linear increase of BCP reorganization energy in the range HFX=0.05 to 0.25.

Fig.\ref{fig:autogen_MADN}(d) shows that the energy disorders for the used HFX are smaller compared with that of BCP. And they have a relatively similar range.

Using the energy obtained from PBE0 functional with HFX=0.25 as a reference, the scatter plot in Fig.\ref{fig:E_qmmm_MADN} shows that all HFX values produce molecule energies in the range -0.5 to -1.1 eV. And different HFX has similar molecular energy, as all the points are group close to the diagonal line.

The scatter plots of the electrostatic energy and polarization energy as shown in Fig. \ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} also shows that those two energy terms are similar when HFX varies from 0 to 0.25. That is, there is no obvious small data points deviated from the diagonal line.

@@

Furthermore, the plot comparing  electrostatic energy and polarization energy are shown in Fig.\ref{fig:Estat_qmmm_MADN} and Fig.\ref{fig:Edip_qmmm_MADN}.
The electrostatic energy has a range of 0.1 to -0.6 eV. And there are no small data points deviated from the diagonal line. 
The polarization energy has a range of -0.5 to -0.8 eV. And the data points are again clustered near the diagonal line.

@@

\section{Comparison of Diffusive Charge Velocity Between BCP and MADN}
In this section we compare the diffusive charge velocity between BCP and MADN. 
The following tables show the diffusive charge velocity for BCP and MADN with HFX=0.05, 0.15, 0.25. The situations of using energy disorder and without energy disorder are considered.
For the ToF setting, we investigate the situations where the charge transport direction is along the X-axis, Y-axis and Z-axis, as shown in Table \ref{tab:compare_Lx}, \ref{tab:compare_Ly}, and \ref{tab:compare_Lz}.

>>>>

\begin{document}
\linenumbers
\title{Uncertain Effects of DFT Functionals on Charge Dynamic of Organic Semiconductor }
\author{authors}
\date{\today}
\maketitle
\begin{abstract}

\end{abstract}

@@

The charge dynamics is determined by CTRW transition rates, which depend on the electronic structures.
Since DFT is used to calculate the molecular electronic structures, the unknown exchange-correlation functional in DFT will bring uncertainties to the multiscale model. 
In particular, different DFT functionals contain varying levels of Hartree Fock (HF) to represent the exchange-correlation potential. 
The effect of the uncertainty from the DFT exchange-correlation functional on the multiscale model is not yet explored in literatures. 
The goal of this work is to quantify the uncertainty effect of the DFT exchange-correlation functional on the charge dynamics in OSCs and to study the robustness of the multiscale model, with a particular focus on the uncertainty represented by the HF level.

@@

Specifically, the focus will be placed on following questions: 
\begin{enumerate}
    \item How does HF level change the electronic structures: reorganization energy, distribution of molecule energies and coupling elements? 
    \item How does HF level change the charge mobility?
    \item Which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the charge mobility distribution?
    \item Can we estimate the range of the quantity of interest, given a confidence level?
\end{enumerate}

@@

To calculate $v_\text{SS}$ the steady state distribution $\pi_i$ is required. In continuous time Markov chain, the steady state distribution vector $\vec{\pi}: \pi_i$ is the null-space of $\mathbf{W}-\mathbf{D}$:
\begin{equation}
    (\mathbf{W}-\mathbf{D} )\vec{\pi} = \mathbf{0}
\end{equation}
where $\mathbf{D} = \text{diag}(D_i)$ is the out-degree matrix of $\mathbf{W}$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results on MADN}

In this study, we investigate the hole-transporting organic semiconductor MADN (2-Methyl-9,10-di(naphth-2-yl)anthracene). Essential steps in our multiscale model involve calculating the dipole moment $\mu$ and the isotropic polarizability $P_\text{iso}$ for both neutral and charged states in the optimized geometry MADN molecule. These properties are crucial for evaluating molecular energy contributions from electrostatic and polarization effects.

Figure \ref{fig:autogen_MADN} illustrates the dependence of the dipole moment $\mu$, isotropic polarizability $P_\text{iso}$, reorganization energy $\lambda$, and energy disorder $\sigma(E)$ on the Hartree-Fock exchange (HFX) parameter.

%
\begin{figure}[H]
    \centering
    \includegraphics[width=0.80\textwidth]{figs/MADN_HFX/fig_autogen.pdf}
    \caption{(a) The dipole moment of neutral state MAND molecule $\mu$, (b) isotropic polarizability $P_\text{iso}$, (c) reorganization energies $\lambda$ and (d) energy disorder $\sigma(E)$ as a function of the HFX parameters (denoted by $\alpha$).}
    \label{fig:autogen_MADN}
\end{figure}
%

Figure \ref{fig:autogen_MADN}(a) shows a decrease in the dipole moment with increasing HFX, exhibiting a notable drop at HFX = 0.25.

Figure \ref{fig:autogen_MADN}(b) demonstrates a linear decrease in isotropic polarizability for both neutral and charged MADN states as HFX increases from 0 to 0.25, indicating reduced molecular polarizability.

Figure \ref{fig:autogen_MADN}(c) indicates an increase in reorganization energy $\lambda$ with higher HFX, reflecting greater energy requirements for electronic adjustments during charge transfer. This increase is nonlinear compared to the linear decrease in $P_\text{iso}$.

Figure \ref{fig:autogen_MADN}(d) shows that the energy disorder $\sigma(E)$ for MADN are similar and close to \unit[0.08]{eV} under different HFX values.

The ToF and corresponding diffusive velocity $v_\text{ToF}$ are presented in Table \ref{tab:ToF_MADN_HFX}. For boundary conditions, the \textit{Source} region contains molecules with X-coordinates $0 < r^x_i < 0.5$ nm, and the \textit{Sink} region contains molecules with X-coordinates $8.5 < r^x_i < 9$ nm. We also consider scenarios without energy disorder to model systems where all molecules have uniform energy.

\begin{table}[H]
    \centering
    \begin{tabular}{c c c c c}
    \hline
        $\alpha$ & ToF [s] & $v_\text{ToF}$ [m/s] & ToF(no $E$) [s] & $v_\text{ToF}$ (no $E$) [m/s] \\
    \hline
        0.00 &  $6.4 \times 10^{-9}$ & 1.2 & $1.9 \times 10^{-10}$ & 42 \\
        0.05 & $ 7.9 \times 10^{-9}$ & 1.0 & $4.1 \times 10^{-10}$ & 20 \\
        0.10 & $ 1.6 \times 10^{-8}$ & 0.51 & $4.0 \times 10^{-10} $ & 20 \\
        0.15 & $ 3.0 \times 10^{-8}$ & 0.31 & $4.0 \times 10^{-10} $ & 25 \\
        0.20 & $ 2.1 \times 10^{-8}$ & 0.39 & $4.5 \times 10^{-10}$ & 18 \\
        0.25 & $ 9.5 \times 10^{-8}$ & 0.083 & $7.2 \times 10^{-10}$ & 11 \\
    \hline
    \end{tabular}
    \caption{The ToF and diffusive velocity calculated by ToF along a distance $L_x = 8$ [nm] with and without energy disorder of the MADN system as a function of the HFX. }
    \label{tab:ToF_MADN_HFX}
\end{table}

Table \ref{tab:ToF_MADN_HFX} shows that as HFX increases from 0 to 0.25, the ToF with energy disorder increases by a factor of approximately 15, while without energy disorder, the increase factor is about 4. This increase in ToF is attributed to the rise in $\lambda$, changes in molecular energies, and variations in coupling elements.

Figure \ref{fig:E_qmmm_MADN} presents a scatter plot comparing the site energies of MADN molecules across different HFX values, using HFX = 0.25 (PBE0 functional) as a reference. The energies consistently fall within the range of -0.5 to -1.1 eV, with data points clustering near the diagonal line, indicating similar molecular energies regardless of HFX variation.

@@

Figures \ref{fig:Estat_qmmm_MADN} and \ref{fig:Edip_qmmm_MADN} show that both electrostatic and polarization energies remain consistent across HFX values from 0 to 0.25, further clustering near the diagonal.

@@

The electrostatic energy ranges from 0.1 to -0.6 eV, while polarization energy spans -0.5 to -0.8 eV.  Similar to the molecule energy, the data points are clustered near the diagonal line. 
The standard deviations of the electrostatic energy are 0.099, 0.094, 0.099, 0.11, 0.10, \unit[0.10]{eV}, and the standard deviations of the polarization energies are 0.044, 0.043, 0.043, 0.047, 0.045, \unit[0.045]{eV}. So the disorder in electrostatic energies is consistently larger than than in molecule energies, and the palorization effect reduces the electrostatic energy disorder. 
Each individual molecule has similar polarization energies under different HFX calculation, in spite of $P_\text{iso}$ is linearly dependent on HFX.

The coupling element obtained with different HFX for each molecular pair compared to that obtained with HFX=0.25 is shown in the scatter plot Fig. \ref{fig:J_MADN}.
\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\textwidth]{figs/MADN_HFX/scatterJ_all.pdf}
    \caption{Scatter plot of MADN coupling element $\log_{10} J^2$ calculated from different HFX, compared to the polarization energy calculated from HFX=0.25 (The PBE0 functional). The brighter color near the diagonal lines indicates denser population of the molecules.  The top and right histogram show the energy distributions.}
    \label{fig:J_MADN}
\end{figure}

The distribution of $\log_{10} J^2$ has a range of -14 to -2, and for all HFX values, the distribution has a peak at around -5. 
For large values $\log_{10} J^2 < -5$ the coupling element remains consistent across HFX values from 0 to 0.25, while for large values $\log_{10} J^2 > -5$, the calculated coupling elements for a specific molecular pair can have large variation due to HFX values.

In charge transport network, $J^2$ undirectional for a molecular pair, and decays exponentially as the mutual center-of-mass distance increases. The large $\log_{10} J^2$ are usually observed for molecular pairs with small center-of-mass distance. And the charge dynamics is more dominated by those large $\log_{10} J^2$ compared to the small $\log_{10} J^2$.

To determine the range of $\log_{10} J^2$ that are significant for the charge dynamics, a percolation algorithm is performed with procedure as:
\begin{enumerate}
    \item A critical value $J_c$ is chosen,
    \item In graph $\mathbf{G}$ remove all the edges with $J^2 < J_c^2$
    \item Calculate the maximum size $\max({N_\text{sub}})$ of the connected subgraphs
\end{enumerate}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\textwidth]{figs/MADN_HFX/fig_network_all.pdf}
    \caption{The maximum size of the subgraphs obtained in the percolation algorithm as a function of critical value $J_c$. The molecular systems obtained by different HFX are colored according to the legend.}
    \label{fig:J_percolate}
\end{figure}
Figure \ref{fig:J_percolate} shows the dependence of $\max({N_\text{sub}})$ on the critical value $J_c$. When $\log_{10} J_c^2 < -4.5$, $\max({N_\text{sub}})$ is 1000, meaning that removing all the edges with $J^2 < 3.1 \times 10^{-5}$ the 1000 vertexes still form a connected graph. 
But when removing the edges with $J^2 < 3.1 \times 10^{-4}$ ( corresponding to $J_c > -3.5$), the maximum size subgraph is 600, and it quickly decreases as $J_c$ increases, showing a phase transition. 
So the dominated coupling elements are those with $\log_{10} J_c^2 > -4.5$. 
And the variation in small $J$ due to HFX has less impact on the charge dynamics.

In this section we answer the question of how does HF level change the electronic structures and 
how does HF level change the charge mobility. 
In the next section, uncertainty quantification via Monte Carlo method and sensitivity analysis is perform to answer which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the charge mobility distribution. 
And further estimate the range of the quantity of interest, given a confidence level.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{ToF Distribution and Sensitivity Analysis}
The previous section shows that different HFX affect the calculated ToF. In this section, we use the Monte Carlo method to estimate the range of the ToF given a confidence level, followed by a sensitivity analysis to determine which parameter contributes more to the variance of ToF.

\subsection{ToF Distribution}
The ToF is calculated from electronic structure ($E$, $\lambda$ and $\log_{10}(J^2)$) data, that is, ToF is a function with the input of all electronic structure parameters:
\begin{equation}
    \tau = g(x_1,x_2,\cdots, x_N) \; 
\end{equation}
where the parameters $(x_1,x_2,\cdots, x_N)$ represents $(E_i, J_{ij}, \lambda)$ for all $i,j=1,2,\cdots,N$ and $J_{ij}>0$.

Since the exchange-correlation functional is not known and each molecule has a slightly different structure compared to the optimized structure, each parameter $(x_1,x_2,\cdots, x_N)$ has uncertain. 
To estimate the uncertainty, we consider the maximum amount of uncertainties according to the obtained $(E_i, J_{ij}, \lambda)$ with the six different HFX.
To achieve this, each parameter can be modeled as a normal distribution with the mean and standard deviation being the HFX sample mean and standard deviation, respectively.

Then Monte Carlo scheme is used to estimate the distribution of the ToF. The Monte Carlo scheme has the procedure:
\begin{enumerate}
\item For all $i=1,2,\cdots, N$, sample a realization $(x_1,x_2,\cdots, x_N)$ where each parameter $x_i \in (x_1,x_2,\cdots, x_N)$ has the normal distribution $x_i \in \mathcal{N}(\bar{x}_i, \sigma_{x_i})$. 
\item Calculate ToF using the sampled data set $(x_1,x_2,\cdots, x_N)$. 
\item Repeat step 1 and 2 for $N_\text{MC} = 50000$ times to obtain ToFs. Plot the distribution of the ToFs.
\item Fit the distribution of $log_{10}(\text{ToF})$ to Gamma distribution.
\end{enumerate}

The ToF distribution and Gamma fitted results for the MADN systems with energy disorder is shown in Fig.\ref{fig:mle_MADN_withE}.
%
\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\textwidth]{figs/MADN_HFX/fig_mle_MADN_withE.pdf}
    \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional and varying HFX. 
    (a) $P(\log_{10}(\tau)|E_i \text{ uncertain})$, 
    (b) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
    (c) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
    (d) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$. The red star indicates the ToF calculated using the average $\bar{E_i}, \bar{J}_{ij}, \bar{\lambda}$, and the red circles indicate the ToF obtained using different HFX.}
    \label{fig:mle_MADN_withE}
\end{figure}
%

When the energy disorder in MADN system is not considered, that is, all the MADN molecule energy are set to be equal giving $\Delta E=0$, the distribution of ToF is shown in Fig.\ref{fig:mle_MADN_noE}
%
\begin{figure}[H]
    \centering
    \includegraphics[width=0.99\textwidth]{figs/MADN_HFX/fig_mle_MADN_noE.pdf}
    \caption{Distribution of ToFs in the multiscale modeled MADN system using PBE0 functional and varying HFX. Energy disorder is not consider. 
    (a) $P(\log_{10}(\tau)|\lambda \text{ uncertain})$, 
    (b) $P(\log_{10}(\tau)|J_{ij} \text{ uncertain})$, 
    (c) $P(\log_{10}(\tau)|E_i, \lambda, J_{ij} \text{ uncertain})$. The red star indicates the ToF calculated using the average $\bar{E_i}, \bar{J}_{ij}, \bar{\lambda}$, and the red circles indicate the ToF obtained using different HFX.}
    \label{fig:mle_MADN_noE}
\end{figure}
%

Measuring the sensitivity of each electronic parameter to ToF is to measure each electronic parameter's contribution to the variance of ToF. 
That is, if ToF is most sensitive to one parameter, the variance in this particular parameter will contribute most to the ToF variance.
